A general Nullstellensatz for generalized spaces

### 2019-03-17 paper-qcoh.tex
Simpler example

\begin{rem}Theorem~\ref{thm:nullstellensatz} cannot be strengthened to
arbitrary geometric sequents. For instance, in the case that~$\TT$ is the
theory of rings, the internal geometric sequent~$(\top \seq{x\?U_\TT}
\bigvee_{a\?U_\TT} (x = e_a))$ trivially holds for~$U_\TT$. However, this sequent is not
provable modulo~$\ul{\TT}/U_\TT$, as for instance the polynomial algebra~$U_\TT[X]$
does not validate it.\end{rem}

>>>>

\begin{rem}Theorem~\ref{thm:nullstellensatz} cannot be strengthened to
arbitrary geometric sequents. For instance, in the case that~$\TT$ is the
theory of objects, the internal geometric sequent~$(\top \seq{x\?U_\TT}
\bigvee_{a\?U_\TT} (x = e_a))$ trivially holds for~$U_\TT$. However, this sequent is not
provable modulo~$\ul{\TT}/U_\TT$, as for instance the model~$U_\TT \amalg
\{\star\}$ does not validate it.\end{rem}
